Eagle: Making multiple-locus association mapping on a genome-wide scale routine

### 2018-05-08 AM+draft.tex
08 May 18 Prior to working on results section - tidy up

\title{Making multiple-locus association mapping on a genome-wide scale routine}
\author{Andrew W. George$^1$ and Joshua Bowden$^2$}

@@

\subsection{Mouse Study}

@@

The Eagle approach for multiple-locus association mapping is based on building a linear mixed model, iteratively, via forward 
selection.  It is a simplification of a whole-genome method for mapping quantitative trait loci in classic linkage studies \cite{verbyla2007analysis}.
Suppose $s$ iterations of our model building process have already been performed. This means $s$ snp-trait 
associations have been identified.  It also means that $s$ separate genomic regions of interest have been found.  
To perform the $s+1$th  iteration of 
our model building procedure, we do the following.

@@

gocard123

@@

To generate the quantitative trait data, first the number of snp that are to be in complete with an underlying qtl (x) is drawn from a poison distribution with mean equal to 30. Second, x snp loci are select randomly from a scenario?s set of genotype data. Third, the snp values are summed across the selected loci for each individual to generate a vector of n genetic values. Here, each snp is having, roughly, the same effect on the trait, remembering that the maf of a snp also impacts a snps influence on a trait. Fourth, n deviates are drawn from a $N(0,sigma^2_e)$ where sigma_e^2 has been set to yield a trait with a heritability of 0.6. (Put in formula). Fifth, the quantitative trait data is generate as $y = g + e$. In this way, the same genotype data are used, within a scenario, for all replicates. Only the quantitative trait data varies across replicates.

@@

\texbf{GEMMA}

>>>>

\title{Eagle: Making multiple-locus association mapping on a genome-wide scale routine}
\author{Andrew W. George$^1$, Joshua Bowden$^2$, need to sort out the other authors}

@@

\subsection{Mouse Study}
Still to be written.

@@

The Eagle approach for multiple-locus association mapping follows from methods developed for QTL mapping in plant 
populations \cite{verbyla2007analysis} (and some other WGAIM references). 
It is based on building a linear mixed model, iteratively, via forward 
selection.

Suppose $s$ iterations of our model building process have already been performed. This means $s$ snp-trait 
associations have been identified.  It also means that $s$ separate genomic regions of interest have been found.  
To perform the $s+1$th  iteration of 
our model building procedure, we do the following.

@@

@@

To generate the quantitative trait data, first the number of snp that are to be in complete with an underlying qtl (x) is drawn from a poison distribution with mean equal to 30. Second, x snp loci are select randomly from a scenario?s set of genotype data. Third, the snp values are summed across the selected loci for each individual to generate a vector of n genetic values. Here, each snp is having, roughly, the same effect on the trait, remembering that the maf of a snp also impacts a snps influence on a trait. Fourth, n deviates are drawn from a $N(0,sigma^2_e)$ where $\sigma_e^2$ has been set to yield a trait with a heritability of 0.6. (Put in formula). Fifth, the quantitative trait data is generate as $y = g + e$. In this way, the same genotype data are used, within a scenario, for all replicates. Only the quantitative trait data varies across replicates.

@@

\textbf{GEMMA:}  to be done.
